### 2023-09-19 latex/paper/main.tex
minor fixes

    return submatrices
\end{lstlisting}
This is then parallelized by distributing the computation of \textit{get\_square\_submatrices},  creating a further \textbf{remote} auxiliary function, \textit{get\_submatrix\_task}:
\begin{lstlisting}[language=Python, caption={Rank function}]
def get_square_submatrices(self, order):
    data = self.get()
    rows, cols = self.shape()
    futures = []

>>>>

    return submatrices
\end{lstlisting}
This is then parallelized by distributing the computation of \textit{get\_square\_submatrices},  creating a further \textbf{remote} auxiliary function, \textit{get\_submatrix\_task}:
\begin{lstlisting}[language=Python, caption={get\_square\_submatrices}]
def get_square_submatrices(self, order):
    data = self.get()
    rows, cols = self.shape()
    futures = []
